Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-27 src/tex/ms.tex
Update
make Fig. 8 larger
change caption and legend

\begin{figure}[t]
	\script{intrin_space.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/intrin_space.pdf}
	\caption{Distribution of training and validation NR waveforms in the
	$q-\chi_{PN}$ space. The blue stars represent the waveforms used to compute
	the training loss and the orange dots represent the waveforms used for
	validation.}
	\label{fig:intrin_space}
\end{figure}

@@

\begin{figure*}[t]
	\script{all_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/all_quadrants.pdf}
	\caption{Distributions of mismatches for both optimization schemes in all 4 regions of Fig.~\ref{fig:ps_q148_quadrant}. 
	We use a constant PSD to calculate the mismatch and
	$\mathcal{L}_{\mathrm{ave}}$ as the loss function. The medians of each distributions are indicated by dashed
	lines.}
	\label{fig:all_quadrants}
\end{figure*}

\begin{figure}[t]
	\script{ps_q148_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_quadrants.pdf}
	\caption{\textit{Top}: Fractional mismatch change of the validation waveforms ().
	Each quadrant is fitted independently to the NR waveforms listed in Tab.~\ref{tab:quadrants}.
	\textit{Bottom}: Combined distribution of both optimization schemes shown in Fig.~\ref{fig:all_quadrants}.}
	\label{fig:ps_q148_quadrant}
\end{figure}

>>>>

\begin{figure}[t]
	\script{intrin_space.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/intrin_space.pdf}
	\caption{Distribution of training and validation NR waveforms in the
	$q-\chi_{PN}$ space. The blue stars represent the waveforms used to compute
	the training loss, green triangles represent extra training data, and the 
	orange dots represent the waveforms used for validation.}
	\label{fig:intrin_space}
\end{figure}

@@

\begin{figure*}[t]
	\script{all_quadrants.py}
	\centering
	\includegraphics[width=\textwidth]{figures/all_quadrants.pdf}
	\caption{Distributions of mismatches for both split region optimization and all region optimization in all 4 
	regions. We use a constant PSD to calculate the mismatch and
	$\mathcal{L}_{\mathrm{ave}}$ as the loss function. The medians of each distributions are indicated by dashed
	lines.}
	\label{fig:all_quadrants}
\end{figure*}

\begin{figure}[t]
	\script{ps_q148_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_quadrants.pdf}
	\caption{Combined distribution of both optimization schemes shown in Fig.~\ref{fig:all_quadrants}.}
	\label{fig:ps_q148_quadrant}
\end{figure}
